\documentclass{article}
\usepackage{tikz}
\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}

\usepackage{coffee3}



\begin{document}
\title{LaTeX Coffee Stains}
\author{Hanno Rein\\
\texttt{http://hanno-rein.de}\\
Cambridge University}
\renewcommand{\today}{April 3, 2009}
\maketitle

%
% the first parameter is the transparency in the interval [0,1]
% the second parameter is the scale.  normal scale is 1.
% The third paramter is the angle in degrees in the interval [0,360]
%
\cofeA{0.075}{0.5}{90}

\cofeA{1}{1.0}{0}
 
\section{Introduction}
This package provides an essential feature to \LaTeX~that has been missing for too long. It adds a coffee stain to your documents. A lot of time can be saved by printing stains directly on the page rather than adding it manually. You can choose from four different stain types:
\begin{enumerate}
  \item $270^\circ$ circle stain with two tiny splashes 
  \item $60^\circ$ circle stain 
  \item two splashes with light colours
  \item and a colourful twin splash.
\end{enumerate}

\section{Usage}
To use the package, simply place the \texttt{coffee3.sty} file in the directory with all of your 
other \texttt{.tex} files \textit{or} install it properly (consult your distribution's manual). 
Then include the following line in the header of your document:
\begin{verbatim}
\usepackage{coffee3}
\end{verbatim}
To place a coffee stain on a page, put one of the following commands in the source code of the relevant page: 
\begin{verbatim}
\cofeA{alpha}{scale}{angle}
\cofeB{alpha}{scale}{angle}
\cofeC{alpha}{scale}{angle}
\cofeD{alpha}{scale}{angle}
\end{verbatim}
where alpha is the transparency factor $\in [0,1]$. The factor of scale is {\tt scale}, and the standard is {\tt scale}=1, 
and the angle is in degrees $\in [0,360]$. 


If you want to change the position of the stains on the page you have to do some hacking. Have a look at the 
end of the \texttt{coffee3.sty} file. It shouldn't be very hard. 

\section{Copyright}
You can freely distribute this package as I do not believe in imaginary property. All stains are self-made, photographed by myself, processed with gimp and traced with Inkscape.
Donations should be made in coffee only. My address is
\begin{quote}
Hanno Rein\\
DAMTP, CMS\\
Wilberforce Road\\
Cambridge CB3 0WA\\
United Kingdom
\end{quote}
See more coffee stains on the next pages.
\cofeC{0.9}{1}{180}
\newpage
\cofeD{0.4}{0.5}{90}
Coffee is great.
\newpage
\cofeB{0.7}{1}{0}
Coffee will save the world. 

\newpage
\cofeA{0.7}{0.75}{2}
Coffee will save the world. 

\end{document}
